X-Factors: External Influences of a Hockey Goaltender's Performance

### 2025-01-06 paper/paper.qmd
Add files via upload

Shots, defined as any player’s attempt to score by directing the puck at the net, are classified as an event type by the NHL. Events, along with their associated attributes and metadata, are officially recorded by Sportradar, the NHL's data partner, using AI-powered data tools [(@sportradar)]. Events are also counted and verified by official scorekeepers.

@@

Using the statistical programming software R [@citeR] as well as packages [@tidyverse], [@modelsummary] and [@caret], we develop a linear regression model with `GSAx_segment` as the response variable and our outlined factors as predictor variables. The objective of this model is to identify which predictors significantly influence goaltender performance, using p-values to assess significance and coefficients to evaluate the magnitude of their effects.

@@

The following datasheet is provided that provides essential, structured information about the MoneyPuck hockey shot dataset [@data]. It extracts questions from [@gebru2021datasheets] as a resource on information included.

@@

Data was cleaned using [@citeR] and packages [@arrow], [@tidyverse], [@zoo]. Data was tested and analyzed with [@testthat], [@caret], and [@knitr]. Data visualizations were created with [@kableExtra].

>>>>

Shots, defined as any player’s attempt to score by directing the puck at the net, are classified as an event type by the NHL. Events, along with their associated attributes and metadata, are officially recorded by Sportradar, the NHL's data partner, using AI-powered data tools [@sportradar]. Events are also counted and verified by official scorekeepers.

@@

Using the statistical programming software R [@citeR] as well as packages tidyverse [@tidyverse], modelsummary [@modelsummary] and caret [@caret], we develop a linear regression model with `GSAx_segment` as the response variable and our outlined factors as predictor variables. The objective of this model is to identify which predictors significantly influence goaltender performance, using p-values to assess significance and coefficients to evaluate the magnitude of their effects.

@@

The following datasheet is provided that provides essential, structured information about the MoneyPuck hockey shot dataset [@data]. It extracts questions from *Datasheets for Datasets* [@gebru2021datasheets] as a resource on information included.

@@

Data was cleaned using R [@citeR] and packages arrow [@arrow], tidyverse [@tidyverse], zoo [@zoo]. Data was tested and analyzed with testthat [@testthat], caret [@caret], and knitr [@knitr]. Data visualizations were created with kableExtra [@kableExtra].
